\documentclass[letterpaper, 10pt,titlepage]{article}

\usepackage[utf8]{inputenc}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\usepackage{pst-gantt}
\usepackage{pst-tools}
\usepackage[letterpaper, margin=0.75in]{geometry}
\usepackage[TABBOTCAP, tight]{subfig}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true,
  linkcolor  = black
}

\setcounter{secnumdepth}{4}
\def\name{Group 48}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Problem Statement},
  pdftitle = {Capstone Project},
  pdfsubject = {Capstone Project},
  pdfpagemode = UseNone
}



\begin{document}

\begin{titlepage}
\begin{center}
    \Huge
    \textbf{Campus Events Mobile Application}
    \textbf{Capstone Project}\\
    \vspace{1.0cm}
    \large
    Developers: Sung Kim, Xiaoli Sun, Zijian Huang\\
    Client: David Vasquez\\
    \vspace{1.5cm}
    \large
    Instructor: D. Kevin McGrath\\

    \large
    CS 461, Fall 2017, Oregon State University\\    

    \vspace{3.2cm}

    \large
    \underline{Abstract}\\
    \vspace{0.3cm}
    \end{center}
    \large

    \tab For the Campus Event Mobile Application program, the client David Vasquez want to make life more convenient for each students, instructors or even residents live in Corvallis since there are lots of events happen everyday. A great mobile application is useful for every user and improve the quality of life. For an useful application, requirement is much important for not only its developer but also every user who will use it. In this document, the team CEMA will introduce all requirements for this application which our client and audiences hope us to do.
    
    \vspace{0.8cm}
    \vfill
    
\begin{center}    
    Oct 25, 2017

\end{center}
\end{titlepage}


\tableofcontents
\newpage



\section{Introduction}
\subsection{Purpose}
The purpose of the software requirements specification(SRS) is to collect and analyze all relevant information pertaining to the application in development. In SRS, it will describe what the application will do and how it should perform in the hands of a user. We will also include possible concepts that may or may not be developed.

\subsection{Scope}
The team will be developing a mobile application that work on both Android and IOS. The user will be provided with either a list view and/or calendar of the upcoming events, a "Discover" tab to find groups they want to follow, a "Following" tab to manage users current list of groups, and finally a "Profile" tab to edit user information. The application will also provide a secure login. If the application finishes early, the team will develop an administrator website to manage group events.
\subsection{Definitions, Acronyms, and Abbreviations }
\begin{table}[ht]
\begin{tabular}{| l | p{9cm} |}
\hline
\textbf{Term} & \textbf{Definition} \\ \hline
Admin / Administrator & A user with the permissions to modify and publish events for their respective group. \\ \hline
Android & A mobile operating system developed by Google to work on various smart phones and tablets.\\ \hline
Application Program Interface (API) & An interface specifying how software components can integrate with various parts of a project or external resources. \\ \hline
Database & A structured set of data that can be accessed and modified in different ways.\\ \hline
Evently & The current name for the mobile application. May change during development. \\ \hline
Events & A planned public or private occasion sponsored by certain organizations/groups. \\ \hline
iOS & A mobile operating system developed by Apple for use in their Ipod touches, Iphones, and Ipads \\ \hline
Mobile Application & A type of application software designed to run on mobile devices such as a smartphone. \\ \hline
MySQL & An open source relational database management system based on Structured Query Language(SQL) \\ \hline
Structured Query Language (SQL) & A standard language for storing, manipulating and retrieving information from a database. \\ \hline
User & Any person, or robot, that wants to make use of the mobile application. \\ \hline
\end{tabular}
\end{table}                                                


%\subsection{References}
%\vspace{0.3cm}

\subsection{Overview}
Throughout the rest of the document there will be more specific details regarding the mobile application. Along with this information, it will include a Gantt chart to show the schedule during Winter 2017-2018.


\section{Overall Description}
The Oregon State University community is filled with various organizations that hosts multiple events every year. These events can range from large public events such as Football games to smaller career related events such as the Oregon State Fall Career Expo. To expand the number of participants and to get the Corvallis community more involved, Evently will host multiple group events to be displayed to the public. The mobile application will display an interactive calender that will provide the users a way to keep track of all the events they want to see. Also, the users will have access to discover new groups that they can follow and participate with. To ensure user privacy, a secure login will be implemented. This application will reach out to anyone in the Corvallis community looking for something to do. Development of this application will start during Oregon States Universities Winter term, while the developers are taking classes. The time frame to complete this application is approximately three months. Since Evently is not a native OSU application, it will not be branded with the OSU logo. To ensure the application reaches a large audience, Evently will be available for both Android and IOS. 
\section{Specific Requirements}
\subsection{External Interface Requirements}
\subsubsection{Mobile Application User Interface}
A user must be able to view a list of upcoming and past OSU campus events. \\
A user must be able to form a group with other users.\\
A user must be able to update or modify personal information.

\subsubsection{Interface Between Mobile Applications and MySQL Database}
The mobile applications will request campus events data from a JSON based HTTP interface on the MySQL database.

\subsubsection{Interface Between Mobile Applications and OAuth2.0 Server}
The mobile applications will authenticate users' login information using OAuth2.0 through OAuth2.0 server.


\subsection{System Features}
\subsubsection{Mobile Applications}
The application must display a list of upcoming and past OSU campus events.\\
The application must be able to allow users to form groups with other users.\\
The application must be able to allow users to update personal information.\\
The application must have login and logout function.

\subsection{Performance Requirements}
\subsubsection{Information feeding}
A list of upcoming and past OSU campus events must be retrieved from MySQL database and displayed immediately after login.

\subsection{Design Constraints}
The mobile applications must not use OSU as logo.\\
The product must rely on free/libre software, and avoid recurring software license fees.

\subsection{Software System Attributes}
\subsubsection{Mobile Applications}
Application must support both iOS and Android.
\subsubsection{MySQL Database}
Application must retrieve data from MySQL database and store group forming information to it
\vspace{0.5cm}


\section{User Stories}
\subsection{ }
\textbf{\underline{Card}}: As a user, I want to have a personal account which could save my personal information and my own page.\\ 
\textbf{\underline{Conversation}}: The user should have a personal account with a sign up and sign in page. The user can register their own account by using their email and set up their password. Also, the user should have their own personal page which could be used to save their personal information.\\
\textbf{\underline{Confirmation}}: When user open this application at the first time, the application will show the sign up page to create an account. Then they will have their own account.

\subsection{ }
\textbf{\underline{Card}}: As a user, I want the application could have a clear and fashionable interface which could give users a good user experience.\\
\textbf{\underline{Conversation}}: In the application, user will see a clear interface with four main buttons below. It means that this app will put all functions into four different part.\\
\textbf{\underline{Confirmation}}: Developer will design the interface for using mockup to design the UI until to design a perfect mockup. Developer will also try to use four main part to achieve the four buttons below in UI.

\subsection{ }
\textbf{\underline{Card}}: As a user, I want to download this application via an official software store to avoid downloading unsafe application.\\
\textbf{\underline{Conversation}}: Safety in application is the most important thing for every user. An official application Store is a credible method to download any applications. User won't trust and download the application which without a safety store.\\
\textbf{\underline{Confirmation}}: This application will be developed on both IOS and Android platforms and the developer will publish this app on the official app store for each platform like App Store and Google Play.


\section{Gantt Chart}
\newpsstyle{Important}{fillstyle=solid,fillcolor=blue}
\newpsstyle{NotImportant}{fillstyle=vlines}
\begin{center}
 
\begin{PstGanttChart}[unit=2,TaskOutsideLabelMaxSize=1, ChartShowIntervals]{14}{9} 

%------------------------ANDROID----------------------------------
\PstGanttTask[TaskInsideLabel={Android Application}]{0}{9}
\PstGanttTask[TaskOutsideLabel={Environment Set-Up},TaskUnitType=Day]{0}{6}
\PstGanttTask[TaskOutsideLabel={Calender Feature},TaskUnitType=Day]{7}{13}
\PstGanttTask[TaskOutsideLabel={Discover Feature},TaskUnitType=Day]{21}{13}
\PstGanttTask[TaskOutsideLabel={Following Feature},TaskUnitType=Day]{35}{13}
\PstGanttTask[TaskOutsideLabel={Profile Tab},TaskUnitType=Day]{49}{6}
\PstGanttTask[TaskOutsideLabel={Secure Log-in page},TaskUnitType=Day]{56}{6}
%------------------------IOS-----------------------------------
\PstGanttTask[TaskInsideLabel={iOS Application}]{0}{9}
\PstGanttTask[TaskOutsideLabel={Environment Set-Up},TaskUnitType=Day]{0}{6}
\PstGanttTask[TaskOutsideLabel={Calender Feature},TaskUnitType=Day]{7}{13}
\PstGanttTask[TaskOutsideLabel={Discover Feature},TaskUnitType=Day]{21}{13}
\PstGanttTask[TaskOutsideLabel={Following Feature},TaskUnitType=Day]{35}{13}
\PstGanttTask[TaskOutsideLabel={Profile Tab},TaskUnitType=Day]{49}{6}
\PstGanttTask[TaskOutsideLabel={Secure Log-in page},TaskUnitType=Day]{56}{6}


%\PstGanttTask[TaskStyle=Important,TaskOutsideLabel={Task 3}, TaskInsideLabel={\Large\textcolor{white}{\textbf{Important}}}]{2}{5}
%\PstGanttTask[TaskStyle=NotImportant,TaskOutsideLabel={Task 4}]{4}{2}
%\PstGanttTask[TaskOutsideLabel={Task 5}]{5}{2}

\end{PstGanttChart}
\end{center}



\end{document}
